### 2022-11-20 paper.Rmd
tau.test added

>>>>

```{r tau-equivalance, include=F}
observe.refit.2 <- IRT %>% 
  dplyr::select(item1,  item6 , item11 , item15 , item20 , item26 , item31 , item36)
describe.refit.2 <- IRT %>% 
  dplyr::select( item7 ,   item27 , item32 , item37)
awareness.refit.2 <- IRT %>% 
  dplyr::select(Ritem5 , Ritem8 , Ritem13 , Ritem18 , Ritem23 , Ritem28 , Ritem34)
nonjudge.refit.2 <- IRT %>% 
  dplyr::select( Ritem10 ,  Ritem25 , Ritem30, Ritem35 )
nonreact.refit.2 <- IRT %>% 
  dplyr::select(item9 , item19 , item21 , item24 , item29 , item33)

observe_tau<- coefficientalpha::tau.test (observe.refit.2 )
describe_tau <- coefficientalpha::tau.test(describe.refit.2 )
awareness_tau <- coefficientalpha::tau.test(awareness.refit.2 )
nonjudge_tau <- coefficientalpha::tau.test(nonjudge.refit.2 )
nonreact_tau <- coefficientalpha::tau.test(nonreact.refit.2 )

observe_omega <- coefficientalpha::omega(observe.refit.2 )
describe_omega <- coefficientalpha::omega(describe.refit.2 )
awareness_omega <- coefficientalpha::omega(awareness.refit.2 )
nonjudge_omega <- coefficientalpha::omega(nonjudge.refit.2 )
nonreact_omega <- coefficientalpha::omega(nonreact.refit.2 )
